\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry}
\usepackage{multicol}
\usepackage{fontawesome5} % For icons
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

\name{Ahmad Whafa Azka Al Azkiyai}
\address{Jakarta, DKI Jakarta, Indonesia \\ +62 813-6664-9092}
\address{
    \href{mailto:azka.alazkiyai@outlook.com}{azka.alazkiyai@outlook.com} \\ 
    \href{https://www.linkedin.com/in/azka-alazkiyai/}{linkedin.com/in/azka-alazkiyai} \\ 
    \href{https://github.com/azka-alazkiyai}{github.com/azka-alazkiyai}
}

\begin{document}

%----------------------------------------------------------------------------------------
%	PROFESSIONAL SUMMARY
%----------------------------------------------------------------------------------------
\begin{rSection}{Professional Summary}

Published researcher and AI practitioner with 3+ years of experience building and operating enterprise-scale fraud detection systems for major Indonesian financial institutions. Combines deep domain expertise in financial security with hands-on machine learning engineering, having developed production ML pipelines processing millions of real-time transactions. Research interests span \textbf{federated learning security}, \textbf{adversarial machine learning}, and \textbf{privacy-preserving AI} for financial applications. Seeking to advance the field of trustworthy AI systems through applied research.

\end{rSection}

%----------------------------------------------------------------------------------------
%	PUBLICATIONS - Moved up for research focus
%----------------------------------------------------------------------------------------
\begin{rSection}{Publications}

\begin{enumerate}
    \item \textbf{Al Azkiyai, A.W.A.}, Barmawi, A.M., Wahyudi, B.A. (2021). \textit{Improving the Imperceptibility of Pixel Value Difference and LSB Substitution Based Steganography Using Modulo Encoding}. In: Arai, K. (ed) Intelligent Computing. \textbf{Lecture Notes in Networks and Systems}, vol 285. Springer, Cham. 
    \href{https://doi.org/10.1007/978-3-030-80129-8_57}{[DOI]}

    \item Saadah, S., \textbf{Al Azkiyai, A.W.A.} (2020). \textit{Monitoring Financial Stability Based on Prediction of Cryptocurrencies Price Using Intelligent Algorithm}. \textbf{2020 International Conference on Data Science and Its Applications (ICoDSA)}, pp. 1-10. IEEE. 
    \href{https://doi.org/10.1109/ICoDSA50139.2020.9212968}{[DOI]}
\end{enumerate}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------
\begin{rSection}{Experience}

\textbf{Fraud Detection \& AI Systems Consultant} \hfill Sep 2021 -- Dec 2024\\
ITSEC Asia \hfill \textit{Jakarta, Indonesia}

\vspace{0.5em}
\textit{Led fraud detection operations and ML system development for enterprise clients including major banks and payment processors, managing real-time systems processing millions of daily transactions.}

\begin{itemize}
    \itemsep -3pt {}
    
    \item \textbf{ML-Driven Fraud Detection:} Engineered and optimized rule-based and machine learning detection strategies within SAS Fraud Management platform, analyzing transaction patterns to reduce false positive rates while maintaining high fraud capture rates.
    
    \item \textbf{Real-Time Systems at Scale:} Directed 24/7 operations for fraud detection systems serving multiple financial institutions, achieving \textbf{99.987\% SLA compliance} across millions of daily transactions.
    
    \item \textbf{Automated ML Pipeline Development:} Built end-to-end ETL pipelines and data processing automation using Python and Bash, improving real-time fraud monitoring efficiency by \textbf{50\%} and enabling faster model iteration cycles.
    
    \item \textbf{Predictive Analytics \& Pattern Recognition:} Conducted advanced fraud pattern analysis using statistical methods and trend analysis, identifying emerging attack vectors and refining detection thresholds across payment channels.
    
    \item \textbf{System Architecture \& Optimization:} Led database architecture migration from non-partitioned to partitioned IBM DB2, improving query performance and scalability for high-volume transaction processing.
    
    \item \textbf{Security \& Adversarial Analysis:} Performed vulnerability assessments on ML platforms (SAS Fraud Management, SAS Viya), identifying and resolving \textbf{25+ critical security issues} -- experience directly applicable to adversarial ML research.
    
    \item \textbf{Cross-Functional Technical Leadership:} Directed team of four engineers; collaborated with data science, compliance, and IT teams on \textbf{15+ production deployments}; reduced incident response time by \textbf{75\%} (20 min → 5 min).
    
\end{itemize}

\textbf{Software Engineering Intern} \hfill Jun 2019 -- Aug 2019\\
Aruna Indonesia \hfill \textit{Jakarta, Indonesia}
\begin{itemize}
    \itemsep -3pt {}
    \item Developed and implemented comprehensive testing framework for real-time chat application, ensuring system reliability and communication integrity.
\end{itemize}

\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL SKILLS
%----------------------------------------------------------------------------------------
\begin{rSection}{Technical Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{4ex}} p{13cm} }
Machine Learning & PyTorch, TensorFlow, Scikit-learn, XGBoost, Time-Series Forecasting, Deep Learning (CNN, LSTM, GRU), Model Evaluation \& Optimization \\[0.5em]

Fraud \& Security & Real-Time Transaction Monitoring, Anomaly Detection, Pattern Recognition, Risk Scoring, Adversarial Analysis, Vulnerability Assessment \\[0.5em]

Data Engineering & Python, SQL, IBM DB2, PostgreSQL, ETL Pipeline Development, Elasticsearch, Data Preprocessing, Feature Engineering \\[0.5em]

ML Platforms & SAS Fraud Management, SAS Viya, SAS Visual Analytics, MLflow, Jupyter \\[0.5em]

Research Areas & Federated Learning, Privacy-Preserving ML, Cryptographic Methods, Steganography, Adversarial Machine Learning \\[0.5em]

Tools \& Infrastructure & Git, Docker, Linux (RHEL), Bash Scripting, Power BI, Technical Documentation
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\begin{rSection}{Education}

\textbf{Telkom University} \hfill Bandung, West Java, Indonesia\\
\textbf{Bachelor of Informatics} | GPA: \textbf{3.82/4.00} \hfill Feb 2021

\begin{itemize}
    \itemsep -3pt {}
    \item \textbf{Thesis:} \textit{Improving the Imperceptibility of Pixel Value Difference and LSB Substitution Based Steganography Using Modulo Encoding} -- Published in Springer LNNS
    \item \textbf{Advisor:} Prof. Ir. Ari Moesriami Barmawi, M.Sc., Ph.D.
\end{itemize}

\vspace{0.3em}
\textbf{Teaching Experience:}
\begin{itemize}
    \itemsep -3pt {}
    \item \textbf{Assistant Lecturer} -- Intelligent Systems, Formal Languages \& Automata Theory \hfill Aug -- Dec 2019
    \begin{itemize}
        \itemsep -2pt {}
        \item Delivered lectures on AI fundamentals, supervised 15+ ML projects, graded 100+ students
    \end{itemize}
    
    \item \textbf{Lab Assistant} -- Algorithms, Databases, Networks, Operating Systems \hfill Aug 2017 -- Dec 2019
    \begin{itemize}
        \itemsep -2pt {}
        \item Mentored 200+ students in programming, debugging, and system design
    \end{itemize}
\end{itemize}

\end{rSection}

%----------------------------------------------------------------------------------------
%	SELECTED PROJECTS
%----------------------------------------------------------------------------------------
\begin{rSection}{Selected Projects}

\textbf{Macroeconomic Forecasting with Deep Learning} \hfill \textit{Python, TensorFlow, Keras}
\begin{itemize}
    \itemsep -3pt {}
    \item Developed hybrid CNN-LSTM and GRU-LSTM architectures for multi-step GDP forecasting using 26 years of Indonesian macroeconomic data (1997--2023)
    \item Achieved \textbf{9.83 RMSE} through systematic hyperparameter optimization, feature engineering (lag creation, windowing), and cross-model benchmarking against traditional statistical methods
\end{itemize}

\vspace{0.3em}
\textbf{Quantitative Stock Analysis \& Prediction System} \hfill \textit{Python, XGBoost, LSTM}
\begin{itemize}
    \itemsep -3pt {}
    \item Built end-to-end pipeline for all IDX-listed stocks: data collection, technical indicator computation (RSI, MACD, EMA, ATR), and ML-based price prediction
    \item Implemented ensemble models (Random Forest, XGBoost, LSTM) with backtesting framework for strategy validation and performance optimization
\end{itemize}

\vspace{0.3em}
\textbf{SignGuard: Federated Learning Defense System} \hfill \textit{Python, PyTorch, PySyft} \hfill \textit{(In Progress)}
\begin{itemize}
    \itemsep -3pt {}
    \item Developing novel defense mechanism combining ECDSA cryptographic signatures with reputation-based systems to detect poisoning attacks in federated learning
    \item Targeting cross-bank fraud detection scenarios with privacy-preserving model aggregation
\end{itemize}

\end{rSection}

%----------------------------------------------------------------------------------------
%	CERTIFICATIONS & LANGUAGES
%----------------------------------------------------------------------------------------
\begin{rSection}{Certifications \& Languages}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{4ex}} l }
IELTS Academic & Overall Band \textbf{7.0} (2024) \\
SAS Certification & Visual Analytics 1 \& 2 for SAS Viya (2023) \\
Languages & Indonesian (Native), English (Professional -- IELTS 7.0) \\
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	RESEARCH INTERESTS (Optional - for academic applications)
%----------------------------------------------------------------------------------------
\begin{rSection}{Research Interests}

Federated Learning Security $\cdot$ Byzantine-Resilient Distributed ML $\cdot$ Adversarial Machine Learning $\cdot$ Privacy-Preserving AI for Finance $\cdot$ Cryptographic Verification in ML Systems $\cdot$ Trustworthy AI

\end{rSection}

\end{document}
